XXXXX \todo{Le titre !} XXXXX

### 2013-03-24 parts/def-ph.tex
examples + defs

\noindent
The sort of a process $a_i$ is referred to as $\PHsort(a_i)=a$ and the set of sorts present in an action $h\in\PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
Given a state $s\in \PHl$, the process of sort $a\in\PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
If $a_i\in \PHl_a$, we define the notation $a_i\in s \EQDEF \PHget{s}{a}=a_i$.

An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}$, $g$ is not playable in $s$.
%Dans un tel cas, l'état résultant du jeu de l'action $h$ dans $\etat$ est dénoté $(\etat \PHjoue h)$, où $\PHget{(\etat \PHjoue h)}{b} = b_k$ et $\forall c \in \PHs, c \neq b \Rightarrow \PHget{(\etat \PHjoue h)}{c} = \PHget{\etat}{c}$.
%
%An action $h=\PHhit{a_i}{b_j}{b_k} \in\PHa$ is \emph{playable} in $s \in L$ if and only if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$.
In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, that is $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.

\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities, where:
  $$\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$$
  and:
  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$

  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
\end{definition}

@@

\subsection{Modeling cooperation.}
\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
As described in \cite{PMR10-TCSB}, the cooperation between processes to make another bounce can be
expressed in PH by building a \emph{cooperative sort}.
\pref{fig:PH-cooperativity} shows an example of cooperation between processes $b_1$ and $c_1$ to
make $a_1$ bounce to $a_2$:
a cooperative sort $bc$ is defined with 4 processes (one for each sub-state of the presence of
processes $b_1$ and $c_1$).
For the sake of clarity, the $bc$ processes are indexed using the sub-state they represent.
Hence, $bc_{01}$ represents the sub-state $\PHstate{b_0,c_1}$, and so on.
Each process of sort $b$ and $c$ hit $bc$ to make it bounce to the process reflecting the status of the sorts $b$
and $c$ (e.g., $\PHfrappe{b_1}{bc_{00}}{bc_{10}}$ and $\PHfrappe{b_1}{bc_{01}}{bc_{11}}$).
Then, it is the process $bc_{11}$ which hits $a_1$ to make it bounce to $a_2$ instead of the
independent hits from $b_1$ and $c_1$.

\begin{figure}[p]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
\TSort{(0,0)}{b}{2}{t}
\TSort{(0,-3.8)}{c}{2}{b}
\TSort{(4.5,-3)}{a}{3}{r}

@@

\caption{\label{fig:PH-cooperativity}
\towrite{Ajouter priorités}
A PH modeling a cooperativity between $b_1$ and $c_1$ to make
$a_1$ bounce to $a_2$.
Actions involving $b_1$ or $c_1$ are in thick lines.
}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(2,0)}{b}{2}{r}
    \TSort{(4,0)}{c}{2}{r}

@@

    \path[bounce, bend left]
    \TBounce{b_0}{}{b_1}{.south west}
    \TBounce{c_1}{}{c_2}{.south west}
    ;
    \path[bounce, bend right]
    \TBounce{c_1}{}{c_0}{.north west}
    ;
  \end{tikzpicture}
  \label{fig:ph-concb}
  \caption{A simple PH example depicting “forward concurrency” between two actions belonging to different classes of priorities.}
\end{figure}

@@

Prédécesseurs prioritaires :
$$\Vs(a) = \{ b \in \PHs \mid \PHh^1(b, a) \neq \emptyset \}$$
$$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$

Sorte coopérative :
$a$ is a well-formed cooperative sort iff:
\begin{itemize}
  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
  \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
\end{itemize}

Composant :
$a$ is a well-formed component iff:
\begin{itemize}
  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
\end{itemize}

>>>>

\noindent
The sort of a process $a_i$ is referred to as $\PHsort(a_i)=a$ and the set of sorts present in an action $h\in\PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
Given a state $s\in \PHl$, the process of sort $a\in\PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
If $a_i\in \PHl_a$, we define the notation $a_i\in s \EQDEF \PHget{s}{a}=a_i$.
We define the semantics of actions in a Process Hitting model in \pref{def:play}.

\begin{definition}
\label{def:play}
  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
\end{definition}

\begin{definition}[Scenario ($\Sce$)]
\label{def:scenario}
  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all scenarios is noted $\Sce$.
\end{definition}

\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities:
  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$,
  with:
  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
  Furthermore, we denote: $\restriction{\Sce}{n}$ the set of scenarios of actions of $\restriction{\PHa}{n}$.
%  
%  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
\end{definition}

@@

\subsection{Modeling cooperation}
\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
As described in \cite{PMR10-TCSB}, the cooperation between processes to make another bounce can be
expressed in PH by building a \emph{cooperative sort}.
\pref{fig:PH-cooperativity} shows an example of cooperation between processes $b_1$ and $c_1$ to
make $a_1$ bounce to $a_2$:
a cooperative sort $bc$ is defined with 4 processes (one for each sub-state of the presence of
processes $b_1$ and $c_1$).
For the sake of clarity, the $bc$ processes are indexed using the sub-state they represent.
Hence, $bc_{01}$ represents the sub-state $\PHstate{b_0,c_1}$, and so on.
Each process of sort $b$ and $c$ hit $bc$ to make it bounce to the process reflecting the status of the sorts $b$
and $c$ (e.g., $\PHfrappe{b_1}{bc_{00}}{bc_{10}}$ and $\PHfrappe{b_1}{bc_{01}}{bc_{11}}$).
Then, it is the process $bc_{11}$ which hits $a_1$ to make it bounce to $a_2$ instead of the
independent hits from $b_1$ and $c_1$.

\begin{figure}
  \centering
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(0,4)}{b}{2}{l}
    \TSort{(6,2)}{c}{2}{r}

    \TSetTick{ab}{0}{00}
    \TSetTick{ab}{1}{01}
    \TSetTick{ab}{2}{10}
    \TSetTick{ab}{3}{11}
    \TSort{(3,1)}{ab}{4}{l}

    \THit{a_0}{prio}{ab_3}{.west}{ab_1}
    \THit{a_0}{prio}{ab_2}{.west}{ab_0}
    \THit{a_1}{prio}{ab_1}{.west}{ab_3}
    \THit{a_1}{prio}{ab_0}{.west}{ab_2}

    \THit{b_0}{prio}{ab_3}{.west}{ab_2}
    \THit{b_0}{prio}{ab_1}{.west}{ab_0}
    \THit{b_1}{prio}{ab_2}{.west}{ab_3}
    \THit{b_1}{prio}{ab_0}{.west}{ab_1}

    \THit{a_1}{selfhit}{a_1}{.west}{a_0}
    \THit{b_1}{selfhit}{b_1}{.west}{b_0}
    \THit{a_0}{bend left}{b_0}{.south west}{b_1}
    \THit{b_0}{bend right=60}{a_0}{.west}{a_1}

    \THit{ab_3}{}{c_0}{.west}{c_1}

    \path[bounce, bend right]
      \TBounce{ab_3}{}{ab_1}{.north west}
      \TBounce{ab_2}{}{ab_0}{.north west}
      \TBounce{ab_3}{}{ab_2}{.north west}
      \TBounce{ab_1}{}{ab_0}{.north west}
    ;
    \path[bounce, bend left]
      \TBounce{ab_1}{}{ab_3}{.south west}
      \TBounce{ab_0}{}{ab_2}{.south west}
      \TBounce{ab_2}{}{ab_3}{.south west}
      \TBounce{ab_0}{}{ab_1}{.south west}
    ;
    \path[bounce, bend right]
      \TBounce{a_1}{}{a_0}{.north west}
      \TBounce{b_1}{}{b_0}{.north west}
    ;
    \path[bounce, bend left]
      \TBounce{a_0}{}{a_1}{.south west}
      \TBounce{b_0}{}{b_1}{.south west}
    ;
    \path[bounce, bend left]
      \TBounce{c_0}{}{c_1}{.south west}
    ;
  \end{tikzpicture}
  \label{fig:ph-livelock}
  \caption{An example of PH model with three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).}
\end{figure}

\begin{comment}
\begin{figure}[p]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
\TSort{(0,0)}{b}{2}{t}
\TSort{(0,-3.8)}{c}{2}{b}
\TSort{(4.5,-3)}{a}{3}{r}

@@

\caption{\label{fig:PH-cooperativity}
\towrite{Ajouter priorités}
A PH modeling a cooperativity between $b_1$ and $c_1$ to make
$a_1$ bounce to $a_2$.
Actions involving $b_1$ or $c_1$ are in thick lines.
}
\end{figure}
\end{comment}

\begin{comment}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(2,0)}{b}{2}{r}
    \TSort{(4,0)}{c}{2}{r}

@@

    \path[bounce, bend left]
    \TBounce{b_0}{}{b_1}{.south west}
    \TBounce{c_1}{}{c_2}{.south west}
    ;
    \path[bounce, bend right]
    \TBounce{c_1}{}{c_0}{.north west}
    ;
  \end{tikzpicture}
  \label{fig:ph-concb}
  \caption{A simple PH example depicting “forward concurrency” between two actions belonging to different classes of priorities.}
\end{figure}
\end{comment}

@@

\paragraph{2 priorities}
In this paper, we only consider Process Hitting models with 2 priorities.

Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
\begin{definition}
\label{def:chainsactions}
  We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
  \begin{align*}
  \PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
  \end{align*}
\end{definition}
\begin{definition}
\label{def:neighbors}
  The set of neighbor sorts $\Vs(a)$ of a given sort $a$ is the set of sorts that can interact with it through actions of priority $1$.
  The set of neighbor actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
  $$\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}$$
  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
\end{definition}

In \pref{def:cs} and \pref{def:component} we define the notion of well-formed component and cooperative sort.
A sort $a$ is a well-formed component iff
it is hit only by actions of priority $2$.
A cooperative sort $a$ is well-formed iff
it is hit only by actions of priority $1$,
if any sub-state of its neighborhood is represented by at least one local steady state in this sort,
and if any of its processes represents at least one sub-state of its neighborhood.
\begin{definition}
\label{def:component}
  A sort $a \in \PHs$ is said to be a well-formed component iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
  \end{itemize}
\end{definition}
\begin{definition}
  \label{def:cs}
  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
  \begin{itemize}
    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) \neq \emptyset$
    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, a_i \in \pfp_s(a)$
  \end{itemize}
\end{definition}

### 2013-03-24 parts/sa.tex
examples + defs

\begin{definition}[Scenario ($\Sce$)]
\label{def:scenario}
  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all scenarios is noted $\Sce$.
%  $\supp(\delta)$ and $\ceil(\delta)$ renvoient respectivement aux premiers et
%  derniers processus de chaque sorte.
%  \begin{align}
%  &\supp(\delta) = \{p\in\Proc\mid \sort(p)\in\sort(\delta) \wedge
%                        p = \first_{\sort(p)}(\delta) \}\enspace,
%  \eqlabel{support}
%  \\
%  &\ceil(\delta) = \{p\in\Proc\mid \sort(p)\in\sort(\delta) \wedge
%                        p = \last_{\sort(p)}(\delta) \}\enspace.
%  \eqlabel{ceil}
%  \end{align}
\end{definition}

@@

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
\end{proof}

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,right of=c01] (c01s) {};
    \node[Aproc,right of=c01s] (b1) {$b_1$};
    \node[Aobj,right of=b1] (b11) {$\PHobj{b_1}{b_1}$};
    \node[Asol,right of=b11] (b11s) {};
    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Anos,right of=b01] (b01nos) {$\bottom$};

@@

    \path
    (c2) edge (c12) edge (c22) edge (c02)
    (c22) edge (c22s)
    (c12) edge (c12s)
    (c12s) edge (b1)
    (b1) edge (b01)
    (b01) edge (b01s)
    (b01s) edge (a1)
    (a1) edge (a11)
    (a11) edge (a11s)
    ;
  \end{tikzpicture}
  \label{fig:sa-concb}
  \caption{The local causality graph of the PH in \pref{fig:ph-concb}.}
\end{figure}

>>>>

\begin{definition}[Scenario ($\Sce$)]
\label{def:scenario}
  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
  The set of all scenarios is noted $\Sce$.
\end{definition}

@@

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
\end{proof}

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};

    \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
    \node[Aobj,below right of=ab11] (ab0111) {$\PHobj{ab_{01}}{ab_{11}}$};
    \node[Asol,below of=ab0111] (ab0111s) {};
    \node[Aobj,below of=ab11,node distance=2.5cm] (ab0011) {$\PHobj{ab_{00}}{ab_{11}}$};
    \node[Asol,below of=ab0011] (ab0011s) {};
    \node[Aobj,below left of=ab11] (ab1011) {$\PHobj{ab_{10}}{ab_{11}}$};
    \node[Asol,below of=ab1011] (ab1011s) {};

    \node[Aproc,below of=ab0111s] (a1) {$a_1$};
    \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
    \node[Asol,below of=a11] (a11s) {};
    \node[Aobj,below right of=a1] (a01) {$\PHobj{a_0}{a_1}$};
    \node[Asol,below of=a01] (a01s) {};
    \node[Aproc,below of=a01s] (b0) {$b_0$};
    \node[Aobj,below of=b0] (b00) {$\PHobj{b_0}{b_0}$};
    \node[Asol,below of=b00] (b00s) {};
    \node[Aobj,below right of=b0] (b10) {$\PHobj{b_1}{b_0}$};
    \node[Asol,below of=b10] (b10s) {};

    \node[Aproc,below of=ab1011s] (b1) {$b_1$};
    \node[Aobj,below of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Asol,below of=b01] (b01s) {};
    \node[Aproc,below of=b01s] (a0) {$a_0$};
    \node[Aobj,below of=a0] (a10) {$\PHobj{a_1}{a_0}$};
    \node[Asol,below of=a10] (a10s) {};

    \path
    (c1) edge (c01)
    (c01) edge (c01s)
    (c01s) edge (ab11)
    (ab11) edge (ab0011) edge (ab0111) edge (ab1011)
    (ab0011) edge (ab0011s)
    (ab1011) edge (ab1011s)
    (ab0111) edge (ab0111s)

    (ab0011s) edge (a1) edge (b1)
    (ab1011s) edge (b1)
    (ab0111s) edge (a1)

    (a1) edge (a01) edge (a11)
    (a01) edge (a01s)
    (a01s) edge (b0)
    (a11) edge (a11s)
    (a0) edge (a10)
    (a10) edge (a10s)

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01)
    (b01) edge (b01s)
    (b01s) edge (a0)
    ;
    \path
    (ab0011) edge[double] (ab0111)
    (ab0011) edge[double,bend right=10] (ab1011)
    (ab1011) edge[double,bend right=10] (ab0011)
    (ab0111) edge[double,bend right=10] (ab1011)
    (ab1011) edge[double,bend right=10] (ab0111)
    ;
    \end{tikzpicture}
  \label{fig:sa-livelock}
  \caption{The local causality graph of the PH in \pref{fig:ph-livelock}.}
\end{figure}

\begin{comment}
\begin{figure}
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,right of=c01] (c01s) {};
    \node[Aproc,right of=c01s] (b1) {$b_1$};
    \node[Aobj,right of=b1] (b11) {$\PHobj{b_1}{b_1}$};
    \node[Asol,right of=b11] (b11s) {};
    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Anos,right of=b01] (b01nos) {$\bottom$};

@@

    \path
    (c2) edge (c12) edge (c22) edge (c02)
    (c22) edge (c22s)
    (c12) edge (c12s)
    (c12s) edge (b1)
    (b1) edge (b01)
    (b01) edge (b01s)
    (b01s) edge (a1)
    (a1) edge (a11)
    (a11) edge (a11s)
    ;
  \end{tikzpicture}
  \label{fig:sa-concb}
  \caption{The local causality graph of the PH in \pref{fig:ph-concb}.}
\end{figure}
\end{comment}
